\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche

### 2012-03-20 article.tex
Removed comments on future research
Added acknowledgements
Removed double spaces

  It has, however, recently been observed that there is a bias towards the
  right leg. The study by Gibbs\cite{rlb} show that there is a total of 152
  kicks in patterns Chon-Ji to Tong-Il. 85 kicks are with the right leg, and
  67 kicks are with the left leg. This means that 56 \% of the kicks are with
  the right leg, and 44 \% with the left leg.

@@

% Future research
%   level of detail (ex. how each technique is divided per stance to say
%   something about what stance is more suited for a technique, or to show a
%   certain technique in a less/not used stance during step sparring to an
%   understanding of techniques beyond patterns

% {left_technique, right_technique} should probably have been tagged
% {both_hands} as well.

% Link to the source code.

% Movements with several blocks should have a tag indicating that there are
% more than one block in the movement.

@@

  Todo.

  % Thanks to Master Nicolaisen (VII. Dan) for pointing out that I already had
  % found a problem statement when I was still looking for one
  %
  % Odd-Magne Hansen (III. Dan) for helping me with the terminology, and
  % general feedback
  %Todo.

>>>>

  It has, however, recently been observed that there is a bias towards the
  right leg. The study by Gibbs\cite{rlb} show that there is a total of 152
  kicks in patterns Chon-Ji to Tong-Il. 85 kicks are with the right leg, and
  67 kicks are with the left leg. This means that 56 \% of the kicks are with
  the right leg, and 44 \% are with the left leg.

@@

@@

  I would like to thank Odd-Magne Hansen (III. Dan), Frøydis Morken and Eirik
  Schwenke for helping me with reviewing and proof-reading the article.
